\documentclass[11pt, letterpaper]{article}  
\usepackage[top=0.3in, bottom=0.3in, left=0.4in, right=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.4pt}  

\renewcommand{\section}[1]{
    \vspace{4pt}
    \textbf{\large #1}\\[-3pt]
    \hrule
    \vspace{2pt}
}

\setlist[itemize]{leftmargin=12pt, itemsep=1.5pt, parsep=0pt, topsep=1pt, font=\small}

\begin{document}

\begin{center}
\textbf{\Large NIDHI KANWAR}\\[2pt]
\href{mailto:nikanwar333@gmail.com}{nikanwar333@gmail.com} \,|\, +91-7300302650 \\
\href{https://www.linkedin.com/in/nidhiikanwar/}{LinkedIn} \,|\, 
\href{https://github.com/Nikanwar3}{GitHub} \,|\, 
\href{https://www.geeksforgeeks.org/user/nikanw92jv/}{GeeksforGeeks} \,|\, 
\href{https://leetcode.com/u/nikanwar3/}{LeetCode}
\end{center}

\section{EDUCATION}
\textbf{Vellore Institute of Technology, Bhopal} \hfill \textit{Aug 2022 -- Jun 2026} \\
Bachelor of Technology (B.Tech) in Computer Science and Engineering \hfill \textbf{CGPA: 8.7 / 10}

\section{PROJECTS}
\textbf{MeetSync -- Real-Time Video Conferencing Platform} \hfill 
\href{https://github.com/Nikanwar3/MeetSync}{GitHub} \\
\textit{React, Node.js, Express, MongoDB, Socket.IO, WebRTC, JWT}
\begin{itemize}
   \item Built a video conferencing app with HD video/audio, screen sharing, in-meeting chat, and guest access using \textbf{WebRTC} mesh and \textbf{Socket.IO}.
   \item Implemented \textbf{JWT-based authentication} with bcrypt password hashing and built RESTful APIs for user and meeting management.
   \item Designed \textbf{MongoDB} schemas with Mongoose for users and meetings; added optional meeting passcode protection.
   \item Developed a Socket.IO signaling server to coordinate WebRTC peer-to-peer connections between participants.
\end{itemize}
\textbf{StayHub -- Full-Stack Holiday Rentals Platform} \hfill
\href{https://github.com/Nikanwar3/stayhub}{GitHub} \\
\textit{Node.js, Express, MongoDB, EJS, Passport.js, Leaflet.js, Cloudinary}
\begin{itemize}
   \item Built a vacation rental platform with property listings, reviews \& ratings, and interactive \textbf{Leaflet.js} maps using MVC architecture.
   \item Implemented session-based authentication with \textbf{Passport.js} and owner-based authorization for protected routes.
   \item Integrated \textbf{Cloudinary} with Multer for image uploads and \textbf{Joi} for server-side data validation with error-handling middleware.
\end{itemize}
\textbf{AI Document Q\&A System} \hfill 
\href{https://github.com/Nikanwar3/AI-Document-Q-A-System}{{GitHub}} \\
\textit{Python, FastAPI, SQLite, PyPDF2, python-docx, HTML/CSS/JavaScript}
\begin{itemize}
   \item Built a document Q\&A system using \textbf{Python} and \textbf{FastAPI} supporting PDF, DOCX, and TXT file uploads with text extraction via PyPDF2 and python-docx.
   \item Designed \textbf{SQLite} schema with documents and chat\_history tables linked by foreign keys to persist conversations.
   \item Created a responsive chat UI with async \textbf{JavaScript} fetch calls for real-time document querying and response rendering.
\end{itemize}

\section{TECHNICAL SKILLS}
\textbf{Languages:} Java, Python, JavaScript \\
\textbf{Frontend:} React.js, HTML, CSS, JavaScript, EJS \\
\textbf{Backend:} Node.js, Express.js, FastAPI, RESTful APIs, JWT \\
\textbf{Databases:} MongoDB, MySQL, SQLite \\
\textbf{Tools:} Git, GitHub, WebRTC, Socket.IO, Postman \\
\textbf{CS Fundamentals:} Data Structures \& Algorithms, OOP, DBMS, Operating Systems

\section{ACHIEVEMENTS}
\begin{itemize}
    \item Solved \textbf{400+ problems} on LeetCode, Codeforces, and GFG covering arrays, strings, trees, graphs, and DP.
    \item \textbf{Pupil (1250)} rating on Codeforces.
\end{itemize}

\section{LEADERSHIP \& EXTRACURRICULARS}
\textbf{Core Member -- Software Development Club, VIT Bhopal} \hfill 
\begin{itemize}
    \item Mentored juniors in \textbf{DSA} and backend development; conducted code review sessions promoting best practices.
    \item Organized technical workshops and coding contests for \textbf{100+ students}.
\end{itemize}

\end{document}
